\documentclass[12pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{fancyhdr}
\usepackage{titlesec}

\pagestyle{fancy}
\fancyhf{}
\lhead{Thera-Hand Project}
\rfoot{\thepage}

\titleformat{\section}{\normalfont\Large\bfseries}{\thesection}{1em}{}
\begin{document}

\begin{center}
    {\Huge\bfseries App Log}
\end{center}
\vspace{1em}
\hrule
\vspace{1em}

\section*{Instructions}
To make a new log entry, copy and paste the block below:

\begin{verbatim}
\section*{YYYY-MM-DD}
[Write a description of what was done. Be concise but specific.]

\vspace{1em}
\noindent\textit{Contributors: Your Name}
\vspace{1em}
\hrule
\end{verbatim}

\vspace{1em}
\hrule
\vspace{1em}

% Example log entries below

\section*{2025-04-10}
Caden developed Thera-App v0.1 with foundational UI and navigation. Jhovanny integrated firebase authentication and database setup. Testing needed for ESP32 connectivity and data handling.

\vspace{1em}
\noindent\textit{Contributors: Caden, Jhovanny}
\vspace{1em}
\hrule

% Add new entries below this line
\section*{2025-04-15}
Established a TA meeting time (Wednesdays 1:10pm). Further development of app frontend while pending mech team's design. Firebase is set up. Jhovanny is working on the backend to ensure data flow from the app to the database. Caden is focusing on UI/UX improvements based on initial feedback.
Akash is 3D printing the new hand wiring device. Jhovanny and Akash communicated about future 3D printing model concepts.

\vspace{1em}
\noindent\textit{Contributors: Caden, Jhovanny, Akash}
\vspace{1em}
\hrule

\section*{2025-04-16}
Had first TA meeting with Charlie. Discussed the app's current state and future goals. Caden presented the app's UI/UX design, and Jhovanny explained the backend setup. Charlie provided feedback on the design and suggested improvements for user engagement. Akash shared updates on the 3D printing process and discussed potential challenges with the mech team.
Caden and Jhovanny are working on implementing Charlie's feedback into the app. 

\vspace{1em}
\noindent\textit{Contributors: Caden, Jhovanny, Akash}
\vspace{1em}
\hrule


\end{document}
